\documentclass[12pt]{wrceletter}


\name{Dennis Evangelista}
\position{Assistant Professor}
%\email{\href{mailto:evangeli@usna.edu}{\emph{evangeli@usna.edu}}}
\email{evangeli@usna.edu}
\telephone{410-293-6132}

\date{\today}

\usepackage{designature}
\signature{\vspace*{-0.7in}\includesignature\\Dennis Evangelista}
%\signature{Dennis Evangelista\\Assistant Professor} % title not needed if in letterhead
\address{\null} %{105 Maryland Avenue\\Annapolis, MD 21402} % leave blank, provided in letterhead
%\longindentation=0in % to change signature to be flushleft

\begin{document}
\begin{letter}{}

% opening here
\opening{To the selection committee:}
\raggedright % if you like this sort of thing
\setlength{\parindent}{15pt} % if you like this sort of thing

I am happy to recommend MIDN 3/C Jae Young Kim for your program. I have known Mr.~Kim for a year as his academic advisor in the Department of Weapons, Robotics, and Controls at the US Naval Academy. Mr.~Kim is a good student in the upper quarter of his class, having just started his major this fall. Though he was not a student in my sections, I am an instructor for two of the classes (EW200 and EW202) that he is taking this year. In addition, I have some experience working with DOE labs from when I was a Naval Reactors engineer as well as some short collaborations with Lawrence Berkeley Lab. 

Mr.~Kim is majoring in Robotics and Controls Engineering and his interests and coursework cover many things that may be of interest for DOE labs. By summer, he will have completed courses in statics, dynamics, programming on embedded microcontrollers, and mechatronics. Students in our major go on to study diverse topics such as mobile robots, autonomous systems, rapid prototyping, biomechanics, to name a few. Our department encourages hands-on and project based learning. I believe Mr.~Kim would do a good job applying what he has learned so far in microcontrollers, mechatronics, and basic control systems to a real research project at a DOE lab over the summer. 

Mr.~Kim is a creative student and is willing to work hard to make his creations work. His project in our introductory class was a mini-golf game with motors and switches, driven by an embedded microcontroller. Working with his group, Mr.~Kim constructed the mechanics of game in a very short time, and applied what he had learned in C to provide for the game's control and interfacing. His willingness to push through things he found challenging to make the project work, even under extreme time pressure, bodes well for his potential performance in a summer internship with you. 

%CQPR 3.57 A in physics and statics, B in ES200, SM316
%

\closing{Very respectfully,} % provides empty 

%\ps{post script here}
%\encl{enclosure here}
\end{letter}
\end{document}